Turbo fast no compromise gravitational wave parameter estimation

### 2022-12-19 src/tex/ms.tex
Add multi-device scaling paragraph

The rest of the paper is structured as follows: We review the basic of PE in
section \ref{sec: PE}. We provide a quick summary of the sampling framework
built on top of \texttt{flowMC} in section \ref{sec: flowMC}. We present
benchmarking result in section \ref{sec: Result}. Finally, we discuss the
implications of this work and directions for future development in section
\ref{sec: Discussion}.

@@

In this section we give a self-contained summary the gravitational-wave
parameter estimation (PE) process.

@@

\section{\texttt{flowMC}}
\label{sec: flowMC}

In this section, we provide a high level summary of how each component in
\texttt{flowMC} benefits the sampling process and their interplay.

@@

% GPU helps pack a shit ton of waveform evaluation
Another benefit accelerator brings is parallel evaluation of waveforms. Since
the waveform models being used in PE are approximants, they can be evaluated at
any given time or frequency independent to what have been generated before the
time or frequency. This means predicting the waveform can be trivially
parallelized over frequency. Together with heterodyned likelihood, we can
evaluate the likelihood at $\mathcal{O}(10^7)$ different locations on an Nvidia
A100 GPU. The high throughput of likelihood evaluations unlocks the potential of
the \texttt{flowMC} sampling algorithms.

@@

% Compared to other works
There are recent works from different groups on speeding up parameter estimation
of gravitational wave, including efficient reparameterization and deep learning
\kw{cite}. While all of these methods are able to get down to minutes-scale parameter
estimation with high fidelity, we would like to highlight the unique strength of
this work, and potential interplay between our work and other's work.
% Stephen's work
Compared to \kw{Stephan's paper}, we do not rely on pre-training the neural
network on a large collection of waveforms and noise realization. This means as
soon as new waveforms models and noise models are available, our algorithm can
already be deployed. Furthermore, our method is essentially an MCMC algorithm,
which inherits the merit of convergence measures in MCMC. As we are only using
the normalizing flow as a proposal distribution, and the normalizing flow is
trained jointly with a local sampler, we do not suffer from overfitting since
our training data is being generated on-the-fly and is always approaching the
target distribution. In this sense, we do not introduce potential extra
systematic error to inference result.

@@

% Multi-device scaling
The current implementation takes one GPU

>>>>

The rest of the paper is structured as follows: We review the basic of PE and
introduce our framework in section \ref{sec: PE}. We present benchmarking
results on both simulated and real data in section \ref{sec: Result}. Finally,
we discuss the implications of this work and directions for future development
in section \ref{sec: Discussion}.

@@

@@

@@

% GPU helps packing a shit ton of waveform evaluation
Another benefit accelerator brings is parallel evaluation of waveforms. Since
the waveform models being used in PE are approximants, they can be evaluated at
any given time or frequency independent to what have been generated before the
time or frequency. This means predicting the waveform can be trivially
parallelized over frequency. Together with heterodyned likelihood, we can
evaluate the likelihood at $\mathcal{O}(10^7)$ different locations on an Nvidia
A100 GPU. The high throughput of likelihood evaluations unlocks the potential of
the \texttt{flowMC} sampling algorithms.

@@

% Compared to other works
There are recent works from different groups on speeding up parameter estimation
of gravitational wave, including efficient reparameterization and deep learning
\kw{cite}. While all of these methods are able to get down to minutes-scale parameter
estimation with high fidelity, we would like to highlight the unique strength of
this work, and potential interplay between our work and other's work.

% Stephen's work
Compared to \kw{Stephan's paper}, we do not rely on pre-training the neural
network on a large collection of waveforms and noise realization. This means as
soon as new waveforms models and noise models are available, our algorithm can
already be deployed. Furthermore, our method is essentially an MCMC algorithm,
which inherits the merit of convergence measures in MCMC. As we are only using
the normalizing flow as a proposal distribution, and the normalizing flow is
trained jointly with a local sampler, we do not suffer from overfitting since
our training data is being generated on-the-fly and is always approaching the
target distribution. In this sense, we do not introduce potential extra
systematic error to inference result.

@@

% Multi-device scaling
One important aspect of modern computing is scalability, meaning it is generally
favorable if one can simply put more computing units in the same problem and
reduce the Wall time. In our case, this means we would like to use more than one
GPU for the same PE process. More GPUs can help in the following ways: first,
more GPUs means we can run more independent chains at the same time, which can
generate more samples faster. But more importantly, as shown in this work and
\kw{cite flowMC?}, more independent chains also helps with reducing the burn-in
time. Parallelizing over the number of chain dimension is trivial and does not
require much change to the current infrastructure. Another way more GPUs can
helps is allowing faster training of larger flow model. While the training time
is not the biggest bottleneck given the flow model used in this study, more GPUs
means we can increase the bandwidth of the flow model by increasing its size
while keeping the training time the same. This helps in capture more complex
geometry in the target space, which can lead to more accurate result in general.
